\documentclass[11pt, a4paper]{moderncv}


\moderncvtheme[grey]{classic}
\usepackage[utf8]{inputenc}
\usepackage[scale=0.87]{geometry}
%\usepackage[scale=0.85, paperheight=75cm, top=2cm, bottom=2cm]{geometry}
\setlength{\hintscolumnwidth}{3.3cm} % if you want to change the width of the column with the dates

\firstname{Philipp}
\familyname{Krenn}
\title{{\href{http://xeraa.net}{http://xeraa.net}}} % optional
\address{Billrothstreet 11/8}{A-1190 Vienna, Austria} % optional
\renewcommand{\mobilesymbol}{}
\mobile{+43 676 3428954} % optional
%\phone{} % optional
\renewcommand{\faxsymbol}{}
\fax{\href{https://twitter.com/xeraa}{@xeraa}} % optional
\renewcommand{\emailsymbol}{}
\email{pk@xeraa.net} % optional
%\homepage{@xeraa} % optional
\extrainfo{\href{https://github.com/xeraa}{https://github.com/xeraa}} % optional
%\photo[84pt]{Picture} % optional
%\quote{} % optional

\nopagenumbers{} % uncomment to suppress automatic page numbering for CVs longer than one page


\begin{document}
\maketitle


\section{Personal Data}
\cventry{Name}{Philipp Krenn, BSc}{}{}{}{}
\cventry{Born}{October 21$^{st}$, 1984}{}{}{}{}
\cventry{Citizenship}{Austria}{}{}{}{}
\cventry{Legal status}{Single}{}{}{}{}


\section{Education}
\cvline{University}{Master studies in \textbf{Software Engineering \& Internet Computing} and \textbf{Information \& Knowledge Management} at the UT Vienna, anticipated graduation in the middle of 2012.}
\cvline{University}{2004 to 2010 bachelor studies in \textbf{Software \& Information Engineering} at the UT Vienna.}
\cvline{High school}{1995 to 2003 GRW Billrothstreet 26--30, A-1190 Vienna: modern language.\newline{} Research paper on "Strategic Information Warfare in Cyberspace".\newline{} School leaving examination passed with distinction on June 16$^{th}$, 2003.}


\section{Employment}
\cventry{since 10/2010}{Course manager}{Splendit IT-Consulting GmbH}{}{}{Sales and consulting, coordination of trainers, management of documents, as well as evaluations.}
\cventry{since 10/2010}{Diplomate}{Ecommerce group}{UT Vienna}{}{Researching current database developments (RDBMS vs. NoSQL) for an industrial Java project, see \href{http://erpel.at}{http://erpel.at}.}
\cventry{since 10/2009}{Web developer}{Men on the Moon GmbH}{}{}{Development of \href{http://www.contentaward.at}{http://www.contentaward.at} and \href{http://www.mediaquarter.at}{http://www.mediaquarter.at} with SilverStripe, MySQL, and jQuery.}
\cventry{05/2009 to 09/2011}{Trainer}{SPC GmbH}{}{}{Courses and workshops for MS Project, project management, XML, and Java.}
\cventry{11/2007 to 09/2010}{Trainer}{Splendit IT-Consulting GmbH}{in Vienna and Salzburg}{}{Courses for JavaScript and jQuery, JSF, JSP~/ Servlet, design patterns, object-orientation, JBoss AS, PostgreSQL, UML2, and WebServices at Oracle GmbH, GNC GmbH, and BTC Weiterbildung GmbH.}
\cventry{08/2004 to 09/2010}{System administrator}{LMC Town to Town Ltd}{}{}{Management of Windows SBS, Windows clients, a Linux firewall, and a Linux webserver.}
\cventry{10/2009 to 06/2010}{Tutor}{Distributed Systems Group}{UT Vienna}{}{Master courses \emph{Software Architectures} and \emph{Design Patterns for Distributed Systems}.}
\cventry{02/2007 to 12/2009}{Web developer}{Farthofer Gastronomie KEG}{}{}{Creation of \href{http:// www.kriterium.at}{http:// www.kriterium.at} with Smarty and jQuery.}
\cventry{02/2009 to 09/2009}{Web developer}{Heumarkt Veranstaltungs GmbH}{}{}{Development of \href{http://www.sandinthecity.at}{http://www.sandinthecity.at} with Drupal, MySQL, and jQuery.}
\cventry{09/2006 to 09/2009}{Web developer}{KLINSER - Direct Trade GmbH}{}{}{Creation of \href{http:// www.lauraleoni.com}{http:// www.lauraleoni.com} with TYPO3 and MySQL.}
\cventry{12/2008 to 05/2009}{Trainer}{ppedv AG}{in Vienna, Munich, and Karlsruhe}{}{Courses for JavaScript, MS Project, and MS SQL Server.}
\cventry{09/2008 to 02/2009}{Web development}{Yves Rocher am Graben and PartyTV GmbH}{}{}{Extensions for \href{http://www.partytv.cc}{http://www.partytv.cc} in PHP and MySQL.}
\cventry{05/2008 to 01/2009}{Web development}{LMC Town to Town Ltd}{}{}{Creation of \href{http://www.towntotown.net/price/}{http://www.towntotown.net/price/} with CakePHP, MySQL, and script.aculo.us.}
\cventry{09/2008 to 12/2008}{System administrator}{KLINSER - Direct Trade GmbH}{}{}{Migration from Windows SBS 2003 to 2008 on Hyper-V.}
\cventry{05/2007 to 09/2007}{Student Developer}{Google Inc.}{Google Summer of Code 2007}{}{"Support for Multiple Databases" for SilverStripe Inc. implemented in PHP~/ PDO, MySQL, PostgreSQL, and MS SQL Server, mentor Brian Calhoun (CEO).}
\cventry{10/2006 to 01/2007}{Web developer}{Splendit IT-Consulting GmbH}{University project}{}{Development of a JEE test application in a team of six students.}
\cvline{}{Various other projects as \textbf{system administrator} (Windows server and client) and \textbf{web developer} (PHP, Drupal, Smarty, MySQL, and PostgreSQL).}


\section{Internships}
\cvline{Summer 2004}{At \emph{Frequentis AG} in the department of \textbf{Accounting and Taxes} for a month.}
\cvline{Summer 2006}{At \emph{Frequentis AG} in the department of \textbf{IT Second Level Support} for six weeks.}


\section{Languages}
\cvline{German}{Native language.}
\cvline{English}{Business fluent.}
\cvline{French}{Good.}


\section{Publications}
\cventry{Book}{SilverStripe 2.4 Module Extension, Themes and Widgets: Beginner's Guide}{Packt Publishing Limited}{978-1849515009 }{publication in May 2011}{Modern web development with SilverStripe, a CMS and framework in PHP5. For further details see \href{https://github.com/xeraa/silverstripe-book}{https://github.com/xeraa/silverstripe-book}.}


\section{Talks and Presentations}
\cvline{11/2010}{Presentation \textbf{Open Source Development Platforms} for \emph{Future Network} at Gentics GmbH.}
\cvline{03/2011}{Presentation on \textbf{Morphia} at \emph{MongoUK2011} in London.}
\cvline{11/2010}{Presentation \textbf{Quality of Open Source} for \emph{Future Network} at Microsoft Austria GmbH.}
\cvline{11/2010}{\emph{IBM Smart Talk} panel discussion on \textbf{Cloud Computing} at the UT Vienna.}


\section{IT Knowledge}
\subsection{Software Development}
\cvline{PHP}{PHP, SilverStripe, Drupal, Smarty, and TYPO3.}
\cvline{Java}{Java, Java, JEE, Wicket, Maven, JUnit as well as TestNG, Eclipse, Jenkins, and Sonar.}
\cvline{Web technologies}{HTML5, XHTML, CSS, JavaScript, and jQuery.}
\cvline{Data exchange}{WebServices (SOAP, REST), JSON, and XML (DTD, Schema, XPath, XSLT).}
\cvline{Databases}{MySQL, MongoDB, ElasticSearch, PostgreSQL, and MS SQL Server.}
\cvline{Misc}{Ruby on Rails, C, Prolog, Haskell, and Shell Scripts.}
\cvline{Tools}{Amazon Web Services (EC2, S3, and Elastic MapReduce), UML2 as well as object-oriented, functional, and logic-oriented programming.}

\subsection{Operating Systems}
\cvline{Microsoft Windows}{Server 2000, 2003, and 2008 (SBS, Standard, as well as Enterprise).\newline{} 2000 Professional, XP, Vista, and 7.}
\cvline{*nix}{Mac OS X, Debian, Ubuntu, and CentOS.}

\subsection{Applications}
\cvline{Microsoft server}{Active Directory, Exchange, VPN, WSUS, and Hyper-V.}
\cvline{Server}{Apache HTTP Server and Tomcat, JBoss AS, GlassFish, and Jetty.}
\cvline{Desktop}{Eclipse, Subversion, Git, \LaTeX, Prezi, Microsoft Project and Visio, as well as GIMP.}
\cvline{Tools}{VMWare, VirtualBox, Webmin, and Parallels Confixx Professional.}

\subsection{Further Training}
\cvline{Project management}{\emph{Cost Estimation, Benchmarking, and Risk Assessment} by the Frauenhofer IESE (2011).}
\cvline{Presentations}{\emph{Train the Trainer 1} and \emph{2} at SPC GmbH (2009 and 2010).}
\cvline{Networks}{\emph{Cisco Certified Network Associate} (CCNA) at Learn \& Use GmbH (2004).}


\section{Additional Qualifications}
\cvline{Core competences}{Analytic and interlaced thinking.\newline{} Structured, exact, and integrative mode of operation.\newline{} Excellent communication skills and team spirit.\newline{} Determination and high interest in new knowledge.}
\cvline{Driver's license}{Vehicle class B (automobile).}
\cvline{Military service}{10/2003 to 05/2004 at Kommando Führungsunterstützung, service rank private first class.}
\cvline{Activities}{Viennese waltz formation at the dancing school Elmayer (since 2009).\newline{} Golf team Wienerberg (since 2001).\newline{} Fitness trainer and oversight at the Sportunion Döbling (2007 to 2009).\newline{} Judo trainer at the Sportunion Döbling (2000 to 2001).\newline{} Participant in school competitions of Latin and Chemistry Olympics (1995 to 1998).}
\cvline{International}{Participant at one national (2001) and two international sessions (Riga 2002 and Gent 2002) of the European Youth Parliament.\newline{} Six weeks in an English boarding school for a half-term (2001).}


\end{document}